Fractional anisotropy as a tracer of cosmic voids

### 2014-09-09 cosmic_voids.tex
new abstract

\begin{abstract}
In the last decades voids have been identified as one of the most 
important features of the Megaparsec Universe, therefore a full 
understanding of their properties is required in order to a proper 
description of the large-scale structure of the Cosmic Web. Identifying
voids in cosmological observations (e.g. redshift galaxy surveys) and 
N-body simulations is hence an important enterprise that must be carried 
out and accordingly, a plethora of different void finding techniques can 
be found in the literature.

We present here a novel approximation for finding voids in cosmological 
simulations based upon two different schemes commonly used for quantifying
the Cosmic Web, i.e. the T-web and the V-web (the so-called web schemes), 
which have proven to be very adequate for that purpose. Unlike previously 
defined void finding techniques based on the density field, we use here 
the fractional anisotropy (FA) computed from the eigenvalues of each web 
scheme and then, through a Watershed Transform, we identify individual 
voids as the catching basins of local minima of the FA field. Like other 
Watershed Transform-based schemes, ours retains the same advantages, i.e., 
it is relatively free-parameter and makes no significant assumptions on 
the shape and structure of voids.

We test our method on the Bolshoi simulation and compare with a
density-based scheme. We find our method gives a better resemblance of 
the visual impression of the distribution of voids within the Cosmic Web, 
in addition to a more robust description of voids as it allows to identify,
in a very clear manner, their outlines as regions where the FA is 
maximized, normally corresponding to walls and filaments. This is mainly 
because of the non-monotonic behaviour of the FA, what allows to use it 
as a sort of one-dimensional tomography of the Cosmic Web.

\end{abstract}

>>>>

\begin{abstract}
Finding and characterizing voids in the large scale structure of the
universe is an important task in cosmological studies. 
In this paper we present a novel approach to find voids in
cosmological simulations.  
It is based on algorithms that use the tidal and the
velocity shear tensors to define the cosmic web.
Voids are identified using the fractional anisotropy (FA) computed
from the eigenvalues of each web scheme. We define the void boundaries
using a watershed transform based on the local minima of the FA; the
boundaries are regions where the FA is maximized, corresponding to
walls and filaments.  This void definition does not have any free
parameter and does not make any assumption on the shape or structure
of the voids.  We test the method on the Bolshoi simulation and report
on the density and velocity profiles for the voids found using this
new scheme.
\end{abstract}
